---
title: "Seguro Popular"
author: "Henry Yang"
format: html
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
```

```{r}
#| cache: true
# Select the key columns we need for analysis
x <- sps |> 
  select(treatment, t2_health_exp_3m, age, sex, education) |> 
  
  # Drop any rows that have missing values (NA) in any of these columns
  drop_na() |> 
  
  # Recode treatment (0/1) to a factor with "Not enrolled" as the first (reference) level
  mutate(treatment = factor(treatment, 
                            levels = c(0, 1), 
                            labels = c("Not enrolled", "Enrolled")))
```

```{r}
ggplot(x, aes(x = treatment, y = t2_health_exp_3m)) +
  # Create a jitter plot to spread out overlapping points
  geom_jitter(alpha = 0.5, width = 0.2) +
  
  # Calculate and plot the mean for each treatment group as a distinct point
  stat_summary(fun = "mean", geom = "point", color = "red", size = 4) +
  
  # Zoom the plot to 0-5000 pesos without discarding data outside that range
  coord_cartesian(ylim = c(0, 5000))
```

```{r}
x |> count(treatment)
```

## Summary
Households enrolling in Seguro Popular might have less of a strain in out-of-pocket medical spending. Out data comes from the Mexican universal health insurance programme in 2005, and we are trying to find the average causal effect of Seguro Popular enrollment on a household’s three-month out-of-pocket health spending. A potential weakness of this model is how it models data that was acquired through voluntary participants, and each survey conducted was self-reported.
