---
title: "Seguro Popular"
author: "Henry Yang"
format: html
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(gt)
library(marginaleffects)
```

```{r}
#| cache: true
# Select the key columns we need for analysis
x <- sps |> 
  select(treatment, t2_health_exp_3m, age, sex, education) |> 
  
  # Drop any rows that have missing values (NA) in any of these columns
  drop_na() |> 
  
  # Recode treatment (0/1) to a factor with "Not enrolled" as the first (reference) level
  mutate(treatment = factor(treatment, 
                            levels = c(0, 1), 
                            labels = c("Not enrolled", "Enrolled")))
```

```{r}
#| cache: true
fit_sp <- linear_reg(engine = "lm") |> fit(t2_health_exp_3m ~ treatment, data = x)
```

```{r}
# Tidy the predictions and plot them with confidence intervals
plot_predictions(fit_sp, condition = "treatment", draw = FALSE) |> 
  ggplot(aes(x = treatment, y = estimate, ymin = conf.low, ymax = conf.high)) +
  
  # Add points for the predicted values
  geom_point(size = 3) +
  
  # Add error bars showing the 95% confidence interval bounds
  geom_errorbar(width = 0.1) +
  
  # Customize labels with variables, takeaway, data source, and readable axis titles
  labs(
    title = "Predicted Health Expenses by Seguro Popular Enrollment Status",
    subtitle = "Enrolled households have slightly lower predicted out-of-pocket health expenses",
    caption = "Source: Seguro Popular Study (sps)",
    x = "Seguro Popular Enrollment Status",
    y = "Predicted Three-Month Health Expenses (Pesos)"
  ) +
  
  # Apply a clean, minimalist style to the plot
  theme_minimal()
```

## Summary
Households enrolling in Seguro Popular might have less of a strain in out-of-pocket medical spending. Out data comes from the Mexican universal health insurance programme in 2005, and we are trying to find the average causal effect of Seguro Popular enrollment on a household’s three-month out-of-pocket health spending. A potential weakness of this model is how it models data that was acquired through voluntary participants, and each survey conducted was self-reported. We modeled the total out-of-pocket medical spending with a Normal Distribution as a function of being enrolled in Seguro Popular. One quantity of interest is that enrolling in Seguro Popular would result in an average out-of-pocket medical spending of 62 pesos less, with a 95% confidence interval of roughly -105 to -22 pesos
